\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-03 paper.tex
Last of the spring cleaning I think….

% [5%] Abstract (75-100 Words Max)

\vfill  %in combination with \newpage this forces the abstract to the bottom of the page
\begin{abstract}
Blizzard Entertainment's World of Warcraft, an online videogame, has a free ``Starter Edition'' which allows players to access the game indefinitely with restrictions. \cite{starterEditionNewsRelease} Studies show a correlation between time spent playing and addiction to Massively Multiplayer Online Role-Playing Games (MMORPGs) like World of Warcraft. \cite{ProblemUsageAmongHighlyEngagedPlayers}\cite{JustAComputerGameRight} Is it ethical for World of Warcraft to use this model?

Based on the Software Engineering Code of Ethics \cite{SECode} Blizzard has acted ethically on all accounts and therefore World of Warcraft's ``Starter Edition'' \emph{is} ethical.
\end{abstract}

\thispagestyle{empty} %remove page number from title page
\newpage

%Create a table of contents with all headings of level 3 and above.
%http://en.wikibooks.org/wiki/LaTeX/Document_Structure#Table_of_contents has info on customizing the table of contents
\thispagestyle{empty}  %Remove page number from TOC
\tableofcontents

\newpage

>>>>

\vfill  %in combination with \newpage this forces the abstract to the bottom of the page
\thispagestyle{empty} %remove page number from title page
\newpage
